---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(jsvm)

# Clear out README figure files before rerendering
readme_figs <- Sys.glob(file.path("man", "figures", "README-*"))
file.remove(readme_figs)
```

# jsvm

jsvm is my personal toolbelt package with functions that I often tend to use or had fun making for some specific purpose.


## Exported functions

* `whoami()`: get filename of executing script when run with Rscript
* `expr2tikz()`: plot the AST of an expression with TikZ (tikz-qtree) in the style of the figures in [Advanced R: Expressions](https://adv-r.hadley.nz/expressions.html)

## Examples

`expr2tikz` creates a tikz string, that (when using the LaTeX package [tikz-qtree](https://ctan.org/pkg/tikz-qtree)) produces a graph representing the abstract syntax tree of an expression, optionally saving the figure as either a pdf or png.

```{r expr2tikz, fig.align='center', out.width='30%'}
filename <- file.path("man", "figures", "README-expr2tikz.png")
expr2tikz(y <- x * 2, filename)
knitr::include_graphics(filename, dpi = 600)
```

More functions and examples to come...